\sysfull

### 2018-04-17 paper/coalescing.tex
Fig 5 updated
minor modifications

%         \While{$\texttt{true}$}
% 	        \State $ B_\text{c} \gets B$
% 	        %
% 	        \While{$ B_\text{c} > 0$}
% 		        \State \Call{execute\_task}{$T_\texttt{i}$}
% 		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
% 		        \State $B_\text{c} \gets B_\text{c} - W$
% 				\State $H_\text{c} \gets H_\text{c} + W$
% 	        \EndWhile
% 	        %
% 	         \State $B \leftarrow $ \Call{$f_\text{compl}$}{B, $H_\text{c}$,$H_\text{p}$}
% 	        \State \Call{commit\_to\_fram}{\null}
%         \EndWhile
% 	\end{algorithmic}
% \end{algorithm}
% %
% To describe the proposed strategies we will use the following parameters:
% \begin{itemize}
% \item target budget $B$: total number of static tasks to be coalesced.
% \item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
% \item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
% \end{itemize}
%
%
% Modifiying Carlo's pseudo code a little 
\begin{algorithm}[t]
	\caption{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing
strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i^{th}$ task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

\subsubsection{Energy-oblivious Coalescing (EB)}
\label{subsec:energyBlind}

@@

\subsubsection{History-Guided Coalescing (HG)}
\label{subsec:energyAware}
The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EB coalescing strategy.  
%
EA gives each task unity weight, as with EB.  
%
HG differs from EB in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i^{th}$ execution period, which has a history
value of $H^{(i)} = 6$.  $B$ is initially three and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$.  HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.

\begin{wrapfigure}{}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/energy-aware-coal.pdf}
	\caption{placeholder}
	\label{fig:energyAware}
\end{wrapfigure}

@@

The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EB and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.

Instead, WHG associates a non-unity weight with each task in the program. 
%
WHG tracks the sum of the weights of tasks in a coalesced sequence of tasks.
%
When the sum of weights reaches $B$, the target, WHG commits the coalesced
task.
%
WHG differs extends EB and HG to explicitly account for the variation in energy
cost of a program's tasks, eliminating the assumption that all tasks do the
same work, which is a key limitation.
%
WHG has the same characteristic operations as HG, except that
$f_\text{weight}(T_\text{i}) = W_\text{i}$.

>>>>

%         \While{$\texttt{true}$}
% 	        \State $ B_\text{c} \gets B$
% 	        %
% 	        \While{$ B_\text{c} > 0$}
% 		        \State \Call{execute\_task}{$T_\texttt{i}$}
% 		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
% 		        \State $B_\text{c} \gets B_\text{c} - W$
% 				\State $H_\text{c} \gets H_\text{c} + W$
% 	        \EndWhile
% 	        %
% 	         \State $B \leftarrow $ \Call{$f_\text{compl}$}{B, $H_\text{c}$,$H_\text{p}$}
% 	        \State \Call{commit\_to\_fram}{\null}
%         \EndWhile
% 	\end{algorithmic}
% \end{algorithm}
% %
% To describe the proposed strategies we will use the following parameters:
% \begin{itemize}
% \item target budget $B$: total number of static tasks to be coalesced.
% \item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
% \item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
% \end{itemize}
%
%
% Modifiying Carlo's pseudo code a little 
%\begin{algorithm}[t]
%	\caption{Coalescing}
%	\label{algo:genCoalescing}
%	\scriptsize
%	%\small
%	\begin{algorithmic}[1]
%        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
%        \State $H \gets 0$ 
%        \While{$\texttt{true}$}       
%	        \State $ i \gets 0$
%	        %
%	        \While{$ i <= B$}
%		        \State \Call{execute\_task}{$T_\texttt{i}$}
%		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
%		        \State $i \gets i + W$
%				\State $H \gets H + W$
%	        \EndWhile
%	        %
%	        \State \Call{commit\_to\_fram}{\null}
%	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
%        \EndWhile
%	\end{algorithmic}
%\end{algorithm}

\begin{wrapfigure}{t}{0.3\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
\end{wrapfigure}
%	\begin{subfigure}[t]{\linewidth}
%	\end{subfigure}
%
%
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing
strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i^{th}$ task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

\subsubsection{Energy-oblivious Coalescing (EO)}
\label{subsec:energyBlind}

@@

\subsubsection{History-Guided Coalescing (HG)}
\label{subsec:energyAware}
The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
%
EA gives each task unity weight, as with EO.  
%
HG differs from EO in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i^{th}$ execution period, which has a history
value of $H^{(i)} = 4$.  $B$ is initially two and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$.  HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.

\begin{wrapfigure}{}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/energy-aware-coal.pdf}
	\caption{The {\em history-guided coalescing} algorithm uses its recent history of execution to estimate the available amount of energy and set the coalescing target accordingly.}
	\label{fig:energyAware}
\end{wrapfigure}

@@

The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EO and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.

Instead, WHG associates a non-unity weight with each task in the program. 
%
WHG tracks the sum of the weights of tasks in a coalesced sequence of tasks.
%
When the sum of weights reaches $B$, the target, WHG commits the coalesced
task.
%
WHG differs extends EO and HG to explicitly account for the variation in energy
cost of a program's tasks, eliminating the assumption that all tasks do the
same work, which is a key limitation.
%
WHG has the same characteristic operations as HG, except that
$f_\text{weight}(T_\text{i}) = W_\text{i}$.

### 2018-04-17 paper/hwswsetup.tex
minor modifications

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} &10 &500 & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} &10 &419 & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} &14 &499 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &5 &227 & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} &8 &516 & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} &181 &4 & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} &10 &428 & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} &14 &426 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} &167 &4 & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}
